---
title: "Developing Data Products Course Project"
author: "Seema"
date: "June 10, 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



## Introduction

This presentation is part of the Developing Data Products Coursera.org course project submission.

It is an R Presentation generated with RStudio.

The Shiny application pitched by this presentation is at https://zipcodeexplorer.shinyapps.io/ZIPCode_Explorer/

The Shiny app source code is available at https://github.com/SimaMN/Developing-Data-Products-course-Week-4-Shiny-Application-and-Reproducible-Pitch

## What is the purpose of the Shiny app?

The Shiny app is based on the interactive map from Washington Post ranking ZIP Codes based on main SES factors. The dataset was accessed from https://github.com/SimaMN/shiny-examples/tree/master/063-superzip-example

```{r cars, echo = TRUE}
allzips <- readRDS("superzip.rds")

head (allzips, 3)

```

## How does it works?

Select a state or City to explore the ZIP ranking and characteristics. 


## Ready to give it a try?

The Shiny application pitched by this presentation is at https://zipcodeexplorer.shinyapps.io/ZIPCode_Explorer/